Untrusted B2B Collaboration using the Blockchain

### 2018-07-25 paper/paper.tex
write paper structure in introduction

>>>>

The rest of this paper is structured as follows: In Section 2 we will discuss concepts and technologies required for our work.
In Section 3 we will present our use case and our solution concept.
Section 4 presents our implementation and tools.
In Section 5 we evaluate our solution.
Finally, Section 6 will present future work and Section 7 will conclude the paper.
